Modelling last glacial cycle ice dynamics in the Alps

### 2017-08-08 articles/cycle/alps-cycle.tex
Rework last section's outline.

    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

    In this section, we compare the model output to geological evidence from
    the last glacial cycle, in terms of LGM extent (Sect.~\ref{sec:extent}),
    ice flow patterns (Sect.~\ref{sec:flow}), ice thickness
    (Sect.~\ref{sec:thickness}), timing (Sect.~\ref{sec:timing}), and the
    number of glaciations (Sect.~\ref{sec:glaciations}).

@@

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM extent}
\label{sec:extent}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Maximum extent is farily well reproduced (Fig.~\ref{fig:lgmvel}a).
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM flow pattern}
\label{sec:flow}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \end{itemize}

    \idea{Add trimline figure in the main text now.}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{LGM ice thickness}
\label{sec:thickness}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

@@

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Timing of the LGM}
\label{sec:timing}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Number of glaciations}
\label{sec:glaciations}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        Modelled extent of glaciation along selected profiles for the Lyon,
        Solothurn, Rhine and Ivrea glaciers.
        \todo{Implement extraction of ice thickness along a more detailed
              profile, and add the other glaciers.}
        \idea{We can also move this as panel b on Fig.~\ref{fig:timing}, with
              profiles drawn on panel a. But then we should probably limit it
              to two glaciers instead of four.}}
      \label{fig:profiles}
    \end{figure}

>>>>

    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:trimlines} -- LGM ice thickness compared to trimlines.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

    In this section, we compare the model output to geological evidence from
    the last glacial cycle, in terms of maximum extent and ice flow patterns
    (Sect.~\ref{sec:flow}), timing of the Last Glacial Maximum
    (Sect.~\ref{sec:timing}), ice thickness (Sect.~\ref{sec:thickness}), and
    glacial cycle dynamics (Sect.~\ref{sec:glaciations}).

@@

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Maximum configuration}
\label{sec:flow}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Maximum extent is reached at 24.57 ka (Fig.~\ref{fig:lgmvel}b).
    \item Some glaciers are not at their maximum (Fig.~\ref{fig:lgmvel}a).
    \item Maximum extent is farily well reproduced (Fig.~\ref{fig:lgmvel}a).
    \item Peripheral ice caps well reproduced (Fig.~\ref{fig:lgmvel}a).
    \item Too much ice in the east (Fig.~\ref{fig:lgmvel}a).
    \item Too little ice in the west (Fig.~\ref{fig:lgmvel}a).
    \item Maximum stages flow pattern is complex (Fig.~\ref{fig:lgmvel}a).
    \item Flow goes sometimes across topography (Fig.~\ref{fig:lgmvel}a).
    \item Transfluences (Montgenèvre, col de l'Échelle, Simplon, Albrun, Gries,
                        (Brünig, Majola, Tagliamento)
    \end{itemize}

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Timing of the Last Glacial Maximum}
\label{sec:timing}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Ice thickness and trimlines}
\label{sec:thickness}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

@@

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Glacial cycle dynamics}
\label{sec:glaciations}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    \begin{itemize}
    \item Rapid variations of total ice volume (Fig.~\ref{fig:lgmvel}b).
    \item Two major glaciations during MIS 4 and 2 (Fig.~\ref{fig:lgmvel}b).
    \item Some glaciers advance many times (Fig.~\ref{fig:profiles}).
    \end{itemize}

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        Modelled extent of glaciation along selected profiles for the Lyon,
        Solothurn, Rhine and Ivrea glaciers.
        \idea{We can also move this as panel b on Fig.~\ref{fig:timing}, with
              profiles drawn on panel a. But then we should probably limit it
              to two glaciers instead of four.}}
      \label{fig:profiles}
    \end{figure}
